\GVN{}-Hoist: Hoisting Computations from Branches

### 2016-08-26 hoist.tex
machine compiler flags

\section{Experimental Evaluation}
\label{sec:experimental-results}
We ran \LLVMTestSuite{} (trunk:d87471f8) with the patch (trunk:86940146) and the
results are listed in Table~\ref{tab:hoist-results}. The table lists the number
of scalars, loads, stores and calls hoisted as well as removed. For each
category, the number of instructions removed is greater or equal to the number
of instructions hoisted because each hoisting is performed only when at least
one identical computation is found.

>>>>

\section{Experimental Evaluation}
\label{sec:experimental-results}
We ran \LLVMTestSuite{} (trunk:d87471f8) with the patch (trunk:86940146). All
the experiments were conducted on x86\_64 Ubuntu-Linux machine and at -Ofast
optimization level.  The results for code-hoisting are listed in
Table~\ref{tab:hoist-results}. The table lists the number of scalars, loads,
stores and calls hoisted as well as removed. For each category, the number of
instructions removed is greater or equal to the number of instructions hoisted
because each hoisting is performed only when at least one identical computation
is found.
